Pteropod exposure analysis

### 2018-03-12 expose.Rmd
remove_rownames fix for shiny server
working on better surviror comparisons

Compare with environmental parameters:
```{r}
expdat <- expdat %>% 
  left_join(envdat, by = 'CTD')
```

@@

A model with environmental variable to model by treatment:
```{r}

selectInput("var", "Choose an environmental variable:", envchr)

>>>>

Compare with environmental parameters:
```{r}

toplo2 <- expdat %>% 
  left_join(envdat, by = 'CTD') %>% 
  unite(`temp, pCO2`, temp_trt, pco2_trt, sep = '/') %>% 
  mutate(
    `temp, pCO2` = factor(`temp, pCO2`, levels = c('lo/lo', 'lo/hi', 'hi/lo' ,'hi/hi'))
  )

toplo3 <- toplo2 %>% 
  gather('var', 'val', -CTD, -`temp, pCO2`) %>% 
  group_by(CTD, var) %>% 
  summarize(
    val = mean(val, na.rm = T)
    ) %>% 
  spread(var, val)

selectInput("vr", "Choose a variable to plot again survivorship:", envchr)

plovr <- reactive({

  names(toplo2)[names(toplo2) %in% input$vr] <- 'xval'

  p <- ggplot(toplo2, aes(x = xval, y = alive)) + 
    geom_point(size = 5, aes(colour = `temp, pCO2`)) + 
    scale_y_continuous('% alive') + 
    theme_bw(base_family = 'serif') + 
    scale_x_continuous(input$vr) + 
    stat_smooth(method = 'lm') +
    ggtitle('all observations')

ploav <- reactive({

  names(toplo3)[names(toplo3) %in% input$vr] <- 'xval'

  p <- ggplot(toplo3, aes(x = xval, y = alive)) + 
    geom_point(size = 5) + 
    scale_y_continuous('% alive') + 
    theme_bw(base_family = 'serif') + 
    scale_x_continuous(input$vr) + 
    stat_smooth(method = 'lm') + 
    ggtitle('Averaged by site')

# ranout <- reactive(lme(alive)

renderPlot({plovr()}, height = 300, width = 600)
renderPlot({ploav()}, height = 300, width = 600)
```

@@

```{r}

selectInput("var", "Choose an environmental variable to model:", envchr)
